When does vapor pressure deficit drive or reduce evapotranspiration?

### 2018-03-21 doc/paper/vpd_et_paper.tex
updated table 1 to write directly from code, should have done this long ago

  \hline
  DBF & deciduous broadleaf forest & 140.7 & 2.63 & 3.12 $\pm$ 0.52 \\
  EBF & evergreen broadleaf forest & 130.3 & 2.56 &  N/A \\
  ENF & evergreen needleleaf forest & 74.3 & 3.45 & 3.30 $\pm$ 0.91 \\
  CRO & cropland & 183.1 & 2.27 & 3.80 $\pm$ 1.01 \\
  CSH & closed shrub & 148.6 & 1.66 & 2.18 $\pm$ 0.44 \\
  GRA & grassland (assumed C3) & 166.0 & 1.92 & 2.68 $\pm$ 0.61 \\
\hline
\end{tabular}
\end{table}

>>>>

  \hline
\input{table_1}
  \hline
\end{tabular}
\end{table}
